RSA + Scalar implicature / TBD

### 2015-11-06 models/RSA+AmbiguousSemantics.Rmd
First steps in prag listener section - image formatting? Incorp images into literal listener sections?

We can approximate the idea of `literal listener` semantics as a distribution over star ratings.
```{r message=FALSE, warning=FALSE}
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", position = "dodge",
      main = "Scalar compatibility with star ratings \n Experiment L0_e8",
      ylab = "P(Word | Rating)",
      data = l0.listener) +
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale)
```

@@

which implicature arises (in this framework). If a listener assumes a speaker is cooperative and obeying the maxims 
```{r multiplot(), results="hide", message=FALSE, warning=FALSE}
multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

```{r, fig.width=16, fig.height=30}
# Code from e9_altsAnalysis.Rmd
d1 = fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T)
d1 = as.data.frame(d1, stringsAsFactors = FALSE)

@@

# Plot findings of salient alternatives for each scale
# -------------------------------------------------------
scales = unique(d$scale)
p1 = ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) +
  ggtitle(paste("Salient alternatives for ", scales[1])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p2 = ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") +
  ggtitle(paste("Salient alternatives for ", scales[2])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p3 = ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") +
  ggtitle(paste("Salient alternatives for ", scales[3])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p4 = ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") +
  ggtitle(paste("Salient alternatives for ", scales[4])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p5 = ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") +
  ggtitle(paste("Salient alternatives for ", scales[5])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

multiplot(p1, p2, p3, p4, p5, cols=1)
```

@@

>>>>

We can approximate `literal listener` semantics as a distribution over star ratings.
```{r message=FALSE, warning=FALSE}
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", position = "dodge",
      main = "Scalar compatibility with star ratings \n Experiment L0_e8",
      ylab = "P(Word | Rating)",
      data = l0.listener) +
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale)
```

@@

which implicature arises (in this framework). If a listener assumes a speaker is cooperative and obeying the maxims 
```{r multiplot(), echo=FALSE}
multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

```{r, fig.width=16, fig.height=30, warning=FALSE}
# Code from e9_altsAnalysis.Rmd
d1 = fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T)
d1 = as.data.frame(d1, stringsAsFactors = FALSE)

@@

# Plot findings of salient alternatives for each scale
# -------------------------------------------------------
scales = unique(d$scale)
p1 = ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[1])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p2 = ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[2])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p3 = ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[3])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p4 = ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[4])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
p5 = ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[5])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

multiplot(p1, p2, p3, p4, p5, cols=1)
```
Clearly some interesting differences between scalar sets. In particular, responses for scales such as `some_all` and `liked_loved` appear to have more clearly defined set of alternatives with high responses for alternatives such as `none` (XX responses) or `most`. Conversely, scales such as `memorable_unforgettable` and `palatable_delicious` have a much longer tail of possible alternatives, with less cleary defined top competitors.

Explanation / Investigation of these differences?

@@

Our `Literal Listener` experimental design involves presenting participants with a star rating and asking for a judgment on the compatibility of a target scalar term with that rating using a binary (yes/no) dependent variable.  While these distributions differ from what we might have proposed from a purely logical interpretation of literal listener semantics (i.e. `some` entails "at least one" and is uniformily compatible across all star ratings >= 1) we do capture the intuition that `some` has some compatibility across all ratings >= 1, but that this compatibility is graded across star ratings, not uniform.

Can we also capture pragmatic enrichment in this current paradigm? Rational Speech-act theory frames language understanding as a special case of social cognition (Goodman & Stuhmuller, 2013) in which a listener must reason about a speaker who must reason about a listener (with an eventual grounding out of the recursion). In order to capture this iterated reasoning process we'll need to extend our paradigm so that participants must consider *what someone else might have meant by an utterance*. This is equivalent to capturing the posterior quantity we're interesed in:

$$p(meaning | utterance)$$

With a slight modification to our current paradigm, we can get estimates of this posterior distribution. Instead of presenting participants with a star rating and target scalar item and ask for a compatbility judgment, we ask participants to reason about the possible meaning of a given scalar term given a speaker utterance. Meaning is again quantified through star ratings.

<center>
<img src="RSA+AmbiguousSemantics_Images/e11_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
</center>
```{r}
#![alt text](RSA+AmbiguousSemantics_Images/e11_example.png)
```
